Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-19 snapshot_system/challenge.tex
wording changes

As we discuss earlier, collocating the backup service on the existing
cloud cluster avoids the extra cost to acquire a dedicated backup facility
and reduces the network bandwidth consumption in transferring the un-deduplicated
raw data for backup. 
%The running of such a service is subject to the resource availability of the system and 
We discuss the design considerations as follows.

% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{itemize}
\item {\em Collocating with cluster-based cloud services.}
We collocate the backup service with other cloud serices in a cluster
and  use a distributed file system~\cite{GFS2004,Hadoop}  to 
store the backup with multiple replicas. 
There can be a concern that storing many versions  of snapshots would
require	a large amount of storage.
The previous research shows the deduplication can compress the backup copies 
effectively in a 10:1 or even 15:1 rage. Assume on the average the compression
ratio is $c$:1.  When the number of versions
saved in the backup storage is $l$  on the average, 
the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
When $l=9$ and $c=13$, storage usage is 40\%. 
That is acceptable given today's cheap cost for disk storage.
In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data
while each machine typically can provide over 10TB storage.
Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
extra space for the backup is not a practical concern.

@@

\item {\em Fault tolerance and isolation.}
The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
and we can use the open-source software to implement such a layer.
When the number of machines failed exceeds the replication degree, there will be
 some data loss.  Storage deduplication worsens the impact of such faults
because  the majority of data snapshots (e.g. over 90\%) is deduplicated
and the corresponding data blocks are shared among VMs.

The previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
studied the solutions  to reduce memory requirement.
They have not considered content sharing affects
fault isolation.
Because a content chunk is compared with a content signature collected from other users,
this artificially creates data dependency among different VM users.
% since storage for shared identical content chunks can become a failure point.
In large scale cloud, node failures happen at daily basis,
the loss of a shared block can affect many users whose snapshots share this 
data block. 
Without any control of such data sharing, we can only increase  
replication for global dataset to enhance the availability,
but this incurs significantly more cost.
Loss of a small number of  shared data blocks can 
cause the unavailability of snapshots for a large number of virtual machines.
Thus a key goal  in our design
is restricting the impact of  data loss to a limited number of VMs. 
It is not desirable that small scale of data failure affects the backup of many VMs.
%when users access snapshots in a recovery process.

@@

%\item {\em Requirement for backup throughput and low computing resource usage}.
Because of collocation of this snapshot service with other existing cloud services, 
%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
%to be processed can be huge. 
the computing resources allocated for a snapshot service is limited
because of its lower priority.  
The key usage of resource for backup is memory for storing and comparing the fingerprints. 
We will consider the approximation techniques with less memory consumption
studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
%and comparison.  This competes memory resource  with the existing VMs.
%Our design is to identify a low-cost and low-profile scheme for deduplication.
%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
A  longer use of bandwidth and computing resource  for backup can create  noticeable  contention with 
the existing cloud, which is not preferred for cloud production system operation. 
Thus it is desirable that backup for all nodes
can be conducted in parallel and in a short period of time,
and any centralized or  cross-machine communication for
deduplication should not become a bottleneck.
For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
the system must finish saving daily snapshots of all VMs in a few hours. 
Often a cloud has a few hours of light workload each day (e.g. midnight),  
which creates an small window for automatic backup.
The backup service can generate hundreds of terabytes of data in such a time window
without optimization and thus the resource content is considered carefully as we design
a fault-resilient cluster-based solution. 
%In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 
%500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours.

@@

With these considerations in mind, we study a cluster-based backup service 
VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
to the existing applications.  
We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
an architecture and implementation design with deletion support.

>>>>

As discussed earlier, collocating the backup service on the existing
cloud cluster avoids the extra cost to acquire a dedicated backup facility
and reduces the network bandwidth consumption in transferring the un-deduplicated
raw data for backup. 
%The running of such a service is subject to the resource availability of the system and 
We discuss the design considerations as follows.

% That arises mainly in Alibaba's Aliyun cloud service.
%concerns
%Base on Aliyun's production environment, the snapshot backup job has to satisfy 
\begin{itemize}
\item {\em Collocating with cluster-based cloud services.}
We collocate the backup service with other cloud serices in a cluster
and use a distributed file system~\cite{GFS2004,Hadoop} to 
store the backup with multiple replicas. 
There might be a concern that storing many versions of snapshots would
go against the purpose of deduplication.
The previous research shows the deduplication can compress the backup copies 
effectively in a 10:1 or even 15:1 rage. Assume on the average the compression
ratio is $c$:1.  When the number of versions
saved in the backup storage is $l$  on the average, 
the amount of storage space in the cluster allocated  for the backup would be $\frac{l}{l+c}$.
For example, when $l=5$ and $c=10$, 33\% of the cluster storage is used for the backup.
When $l=9$ and $c=13$, storage usage is 40\%. 
That is acceptable given today's cheap cost for disk storage.
In the case of Alibaba, each machine hosts 25 VMs on the average and each VM uses 40GB data.
Each machine however can typically provide over 10TB storage.
Thus the normal disk usage  is about 1TB per machine, and adding 30\% to 100\% 
extra space for the backup is not a practical concern, especially with the
added benefits of cheaper running costs and lower network bandwidth requirements.

@@

\item {\em Fault tolerance and isolation.}
The distributed file system~\cite{GoogleFS,Hadoop} provides the replication support
and we can leverage existing open-source software to implement such a layer.
When the number of machines failed exceeds the replication degree, there may be
 some data loss.  Storage deduplication worsens the impact of such faults
because  the majority of each snapshot (e.g. over 90\%) is deduplicated
and the corresponding data blocks are shared among VMs.

Previous work in deduplication~\cite{extreme_binning09,sparseindex09} has
studied the solutions to reduce memory requirements.
One important issue not considered in the previous work is how content sharing affects
fault isolation.
Because a content chunk is compared with a content signature collected from other users,
this artificially creates data dependency among different VM users.
% since storage for shared identical content chunks can become a failure point.
In large scale cloud, node failures happen at daily basis,
the loss of a shared block can affect many users whose snapshots share this 
data block. 
Without any control of such data sharing, we can only increase  
replication for global datasets to enhance the availability,
but this incurs significantly higher costs.
Loss of a small number of shared data blocks can 
cause the unavailability of snapshots for a large number of virtual machines.
Thus a key goal  in our design
is restricting the impact of  data loss to a limited number of VMs. 
It is not desirable that small scale of data failure affects the backup of many VMs.
%when users access snapshots in a recovery process.

@@

%\item {\em Requirement for backup throughput and low computing resource usage}.
Because of collocation of this snapshot service with other existing cloud services, 
%As a large-scale cluster hosting tens of thousand of active VMs everyday,  the amount of data
%to be processed can be huge. 
the computing resources allocated for the snapshot service is limited, especially
because of its lower priority.
The key usage of resource for backup is memory for storing and comparing the fingerprints. 
We will consider the approximation techniques with less memory consumption
studied in~\cite{extreme_binning09,Guo2011} along with the fault isolation consideration discussed below. 
%A snapshot backup service shall not compete cpu, memory, or I/O bandwidth with VMs. 
%Fingerprint-based search does require a significant amount of memory for fingerprint lookup
%and comparison.  This competes memory resource  with the existing VMs.
%Our design is to identify a low-cost and low-profile scheme for deduplication.
%Specifically, the memory usage of snapshot service can never exceed 500MB in any node.
Excessive use of bandwidth and computing resource for backup can create
noticeable contention for resources with the existing cloud, which is not
preferred and may not not be acceptible for production system operation. 
Thus it is desirable that backup for all nodes
can be conducted in parallel and in a short period of time,
and any centralized or cross-machine communication for
deduplication should not become a bottleneck.
For example, in an Aliyun cluster with over 1,000 nodes and each hosts over 25 VMs, 
the system must finish saving daily snapshots of all VMs in a few hours. 
Often a cloud has a few hours of light workload each day (e.g. midnight),  
which creates an small window for automatic backup.
The backup service can generate hundreds of terabytes of data in such a time window
without optimization and thus the resource content is considered carefully as we design
a fault-resilient cluster-based solution. 
%In our typical 1000 nodes cluster, each node hosts 25 VMs, each VM has 40GB of data on average, that translates to backup throughput of 139GB/second, or 
%500TB/hour.  The system must finish saving daily snapshots of all VMs in few hours.

@@

With these considerations in mind, we study a cluster-based backup service 
with VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
to the existing applications.  
We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
an architecture and implementation design with deletion support.
